\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-08-18 tex/ms.tex
tests, text, and bugfixes
unit tests for equations
contrast integral
changing spot param slightly

    \mathbf{x} = \left( \lambda \,\, \phi \,\, \xi \,\, r \right)^\top

@@

    \mathbf{s}(r)

@@

where $\lambda$ is the longitude of a spot, $\phi$ is its latitude, $\xi$
is its contrast, and $r$ is its radius. The vector function $\mathbf{s}(r)$

@@

    p(r \, \big| \, \pmb{\theta}_{r})

@@

    \pmb{\theta}_{r} \right)^\top

@@

    \mathbf{e_1}(\pmb{\theta}_r)

@@

    \mathbf{s}(r) \,
    p(r \, \big| \, \pmb{\theta}_{r}) \,
    \mathrm{d}r
    \mathbf{e_2}(\pmb{\theta}_b, \mathbf{e_1})

@@

    \mathbf{e_3}(\pmb{\theta}_\phi, \mathbf{e_2})

@@

    \mathbf{e_4}(\pmb{\theta}_\lambda, \mathbf{e_3})

@@

@@

    \mathbf{E_1}(\pmb{\theta}_r)

@@

    \mathbf{s}(r) \, \mathbf{s}^\top(r) \,
    p(r \, \big| \, \pmb{\theta}_{r}) \,
    \mathrm{d}r

@@

    \mathbf{E_2}(\pmb{\theta}_b, \mathbf{E_1})
    p(\xi \, \big| \, \pmb{\theta}_b)
    \mathbf{E_3}(\pmb{\theta}_\phi, \mathbf{E_2})

@@

    \mathbf{E_4}(\pmb{\theta}_\lambda, \mathbf{E_3})

@@

@@

%
\section{The Size Integrals: \lowercase{$\mathbf{e_1}$} and $\mathbf{E_1}$}
\label{sec:size}
%
\subsection{Functional form}
\label{sec:size-function}
%
We adopt the following expression for the $n^{\mathrm{th}}$ term in $\mathbf{s}$
in the expansion of a dark, unit contrast circular spot at
$\lambda = \phi = 0$:
%
\begin{align}
    \label{eq:s}
    s_{n}(r) =
    \begin{cases}
        \dfrac{r' \delta_{l0}}{2}
        -\dfrac{r' \left( 2 + r' \right)}
        {2 \sqrt{2l + 1} (1 + r')^{l + 1}}
         & m = 0
        \\
        0
         & \mathrm{otherwise}
    \end{cases}
\end{align}
%
where
$l = l(n), m = m(n)$ (Equation~\ref{eq:lm}) and
$\delta$ is the Kronecker delta. The parameter $r'$ is defined as
%
\begin{align}
    \label{eq:rprime}
    r' \equiv c_0 + c_1 r
    \quad,
\end{align}
%
where $c_0, c_1 > 0$ are scaling constants (defined in more detail below)
and $r \in [0, 1]$ is the normalized spot radius.
The expression in Equation~(\ref{eq:s}) is convenient because it satisfies
five important properties:
%
\begin{enumerate}[itemsep=2pt,parsep=1pt,label=\textbf{\arabic*}]
    \item The surface intensity is azimuthally symmetric about the spot center
    \item The surface intensity monotonically increases away from the spot center
    \item The surface intensity at the spot center is $-1$
    \item The surface intensity at the antipode of the spot center is zero
    \item The size of the spot increases monotonically with $r$
\end{enumerate}
%
These properties may be demonstrated by considering the
expression for the surface intensity at a given polar angle $\theta$ and
azimuth $\varphi$:
%
\begin{align}
    \begin{split}
        I(\theta, \varphi)
        & =
        \sum\limits_{n=0}^\infty
        s_{n} Y_{n}(\theta, \varphi) \\
        & =
        \sum\limits_{n=0}^\infty
        s_{n} \sqrt{2l + 1} \delta_{m0} P_l(\cos\theta)
    \end{split}
\end{align}
%
where $Y_n$ is the spherical harmonic of degree $l(n)$ and order $m(n)$
(see Equation~\ref{eq:lm}),
$P_l$ is the Legendre polynomial of degree $l$,
and we have implicitly
assumed a normalization such that the integral of our expansion over
the unit sphere is $4\pi$.
Note that the expression above is independent of the azimuth $\varphi$,
a consequence of the fact that all harmonics with $m \ne 0$ are zero; this
expansion is therefore azimuthally symmetric about the spot center, as
stated in \textbf{1}.
%
Combining the above expression with Equation~(\ref{eq:s}) and
rearranging, we may write
%
\begin{align}
    \label{eq:Igen}
    I(\theta, \varphi) =
    I(\theta) =
    \dfrac{r'}{2}
    -
    \dfrac{r' \left( 2 + r' \right)}{2 (1 + r')}
    \sum\limits_{l=0}^\infty \left(\dfrac{1}{1 + r'}\right)^l P_l(\cos\theta)
    \quad.
\end{align}
%
The summation in Equation~(\ref{eq:Igen}) has a closed-form expression in
terms of the generating function of the Legendre polynomials:
%
\begin{align}
    \label{eq:gen}
    \sum\limits_{l=0}^\infty t^l P_l(\cos\theta) = \frac{1}{\sqrt{1 + t^2 - 2 t \cos\theta}}
    \quad,
\end{align}
%
so we may express the intensity as a function of polar angle
in the fairly simple form
%
\begin{align}
    \label{eq:Ifinal}
    I(\theta) & = A - \frac{B}{\sqrt{C - \cos\theta}}
    \quad,
    %
    \\
    \intertext{where}
    %
    \begin{split}
        A & = \dfrac{r'}{2}                      \\
        B & = r' (2 + r') \sqrt{\dfrac{1}{8 + 8 r'}} \\
        C & = \dfrac{1 + (1 + r')^2}{2 + 2 r'}
    \end{split}
\end{align}
%
are positive constants.

Differentiating Equation~(\ref{eq:Ifinal}) with respect to $\theta$, we have
%
\begin{align}
    \label{eq:Ideriv}
    \dfrac{\mathrm{d}I(\theta)}{\mathrm{d}\theta} & =
    -\frac{B\sin\theta}{2(C - \cos\theta)^\frac{3}{2}}
    \quad,
\end{align}
%
which is zero only for $\theta = 0$ (for which $I(\theta)$ is
minimized) and $\theta = \pi$ (for which it is maximized). The intensity
therefore increases monotonically from the spot center to the antipode,
as stated in \textbf{2}. The value at the minimum is
%
\begin{align}
    \begin{split}
        I_{\mathrm{min}} & = A - \dfrac{B}{\sqrt{C - 1}} \\
        & = -1
        \quad,
    \end{split}
\end{align}
%
as stated in \textbf{3}, and the value at the maximum is
%
\begin{align}
    \begin{split}
        I_{\mathrm{max}} & = A - \dfrac{B}{\sqrt{C + 1}} \\
        & = 0
        \quad,
    \end{split}
\end{align}
%
as stated in \textbf{4}.
Finally, to show \textbf{5}, let us compute the half width at half minimum
$\Delta\theta$ of the intensity profile:
%
\begin{align}
    A - \dfrac{B}{\sqrt{C - \cos{\Delta\theta}}} =
    -\dfrac{1}{2}
\end{align}
%
Solving for $\Delta\theta$ yields
%
\begin{align}
    \label{eq:hwhm}
    \Delta\theta =
    \cos^{-1} \left[ \dfrac{2 + 3 r' (2 + r')}{2 (1 + r')^3} \right]
    \quad.
\end{align}
%
Differentiation with respect to $r'$ yields
%
\begin{align}
    \dfrac{\mathrm{d}\Delta\theta}{\mathrm{d}r'} =
    \frac{3 r' \left(2 + r'\right)}{\left(1 + r'\right)^4
        \sqrt{\frac{r'^2 \left(2 + r'\right)^2 \left(1 + 2 r'\right)
                \left(3 + 2 r'\right)}{\left(1 + r'\right)^6}}}
    \quad,
\end{align}
%
which is positive definite for all $r' > 0$.

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/hwhm.pdf}
        \oscaption{hwhm}{%
            \emph{Left.} The width $\Delta\theta$
            (Equation~\ref{eq:hwhm}) of the
            spot as a function of the radius parameter $r'$ (bottom axis)
            and the normalized radius $r$ (top axis), computed for
            $l_{\mathrm{max}} = 20$. The green dots indicate the
            minimum value of $r'$ for which the fractional error in the
            spot intensity due
            to the truncated expansion is less than one percent
            and the value of $r'$ corresponding to
            $\Delta\theta = 75^\circ$, respectively. These points correspond to
            the minimum and maximum spot sizes we consider at
            $l_{\mathrm{max}} = 20$
            (blue shading). Note that
            in this regime, the width of the spot scales approximately
            logarithmically with $r'$.
            %
            \emph{Right.} The spot width $\Delta\theta$ below which the
            fractional error in the intensity exceeds various thresholds
            as a function of maximum spherical harmonic degree
            $l_{\mathrm{max}}$. The value of $\Delta\theta$ for a tolerance
            of one percent at $l_{\mathrm{max}} = 20$ is indicated as the
            green dot for reference.
            \label{fig:hwhm}
        }
    \end{centering}
\end{figure}

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/spot_expansion.pdf}
        \oscaption{spot_expansion}{%
            Polar intensity profiles for spots with different normalized
            radii $r$ in the range $(0, 1]$, computed at spherical harmonic
            degree $l_{\mathrm{max}} = 20$. Dotted black curves show profiles
            corresponding to $r < 0$ (corresponding to $r' < c_0$
            in Equation~\ref{eq:rprime}), for which the expansion does
            not converge, leading to ringing and a smaller spot contrast.
            \label{fig:spot_expansion}
        }
    \end{centering}
\end{figure}

It is important to note that the
properties of the spot expansion described above
(in particular its monotonicity and values at the spot center and antipode)
are inherited from the generating function of the Legendre polynomials
(Equation~\ref{eq:gen}). These properties are therefore only rigorously
true when the expansion is taken to spherical
harmonic degree $l_{\mathrm{max}} = \infty$. For truncated expansions,
a value of $r'$ in Equation~(\ref{eq:s}) that is too small will lead
to both ringing and a value at the spot center that is in general larger
than $-1$.

To circumvent these issues, we impose a minimum radius
$r'_{\mathrm{min}}$, whose value is
a function of the degree of the expansion. Since the normalized spot radius
$r$ is defined in the range $[0, 1]$ (Equation~\ref{eq:rprime}), this
minimum value is equal to $c_0$. We compute $c_0 = c_0(l_{\mathrm{max}})$
by numerically finding the
value of $r'$ below which the fractional error in the intensity at the
center of the spot exceeds some threshold, which we take to be 0.01.
Since the half width of the spot $\Delta\theta$ approaches $\nicefrac{\pi}{2}$ as
$r' \rightarrow \infty$ (Equation~\ref{eq:hwhm}), we also impose a
maximum radius $r'_{\mathrm{max}}$, which we define to be the radius
corresponding to
$\Delta\theta = \nicefrac{5\pi}{12} = 75^\circ$. This choice is rather
arbitrary, but motivated by the fact that below this value, $\Delta\theta$
scales approximately logarithmically with $r'$.

The left panel of Figure~\ref{fig:hwhm} shows this scaling. The minimum
and maximum values of $r'$ for $l_{\mathrm{max}} = 20$ are indicated
for reference; these correspond to $r = 0$ and $r = 1$, respectively
(top axis). The right panel of the figure shows the minimum spot half width
$\Delta\theta$ as a function of the spherical harmonic degree of the
expansion for different error thresholds: ten percent (dashed), one
percent (solid), and one part per thousand (dotted).
For $l_{\mathrm{max}} = 20$, the minimum spot half width is about 17$^\circ$.
To model spots smaller than this, one must go to larger $l_{\mathrm{max}}$;
note, however, how slowly $\Delta\theta$ decreases above
$l_{\mathrm{max}} = 20$.

The intensity as a function of polar angle away from the spot center
is shown in Figure~\ref{fig:spot_expansion} for a range of $r$ values.
Three spots with $r < 0$ are also shown; note the presence of
ringing and the fact that the intensity at the spot center is significantly
larger than $-1$.

@@

\subsection{First moment}
\label{sec:size-mom1}
%
The first moment of $\mathbf{s}$ is given by Equation~(\ref{eq:e1}).
We may use Equations~(\ref{eq:s}) and (\ref{eq:pdf_r}) to write the
$n^{\mathrm{th}}$ term of $\mathbf{{e_1}}(\pmb{\theta}_r)$ as
%
\begin{align}
    {e_1}_n(\alpha, \beta)
     & =
    \resizebox{.75\hsize}{!}{$
            \begin{dcases}
                -\dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
                \int\limits_0^1
                \dfrac{
                    (c_0 + c_1 r)
                    r^{\alpha - 1}
                    (1 - r)^{\beta - 1}
                }{2 (1 + c_0 + c_1 r)}
                \mathrm{d} r
                 &
                \qquad
                l = m = 0    \\[2em]
                -\dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
                \int\limits_0^1
                \dfrac{(c_0 + c_1 r) \left( 2 + c_0 + c_1 r \right)r^{\alpha - 1}
                (1 - r)^{\beta - 1}}
                {2 \sqrt{2l + 1} (1 + c_0 + c_1 r)^{l + 1}}
                \mathrm{d} r
                 &
                \qquad
                l > 0, m = 0 \\[2em]
                0
                 &
                \qquad m \ne 0
                \quad.
            \end{dcases}
        $}
\end{align}
%
Thanks to the dependence of the spherical harmonic coefficients on only
powers of $r$ and $(1 + c_0 + c_1 r)$, the integrals above may be expressed in closed
form in terms of the hypergeometric function ${_2F_1}$:
%
\begin{align}
    {e_1}_n(\alpha, \beta)
     & =
    \resizebox{.75\hsize}{!}{$
            \begin{dcases}
                -
                \dfrac{1}{2(1 + c_0)}
                \bigg[c_0H_0^0 + c_1 H_0^1\bigg]
                 &
                \qquad
                l = m = 0    \\[2em]
                -\dfrac{1}{2\sqrt{2l + 1} (1 + c_0)^{l+1}}
                \bigg[
                    c_0(2+c_0)H_l^0
                    +
                    2c_1(1 + c_0)H_l^1
                    +
                    c_1^2 H_l^2
                    \bigg]
                 &
                \qquad
                l > 0, m = 0 \\[2em]
                0
                 &
                \qquad m \ne 0
            \end{dcases}
        $}
\end{align}
%
where we define
%
\begin{align}
    H_j^k & \equiv \left(\prod_{n=0}^{k-1} \lambda_n\right) G_j^k
    \quad.
\end{align}
%
with
%
\begin{align}
    \lambda_n & \equiv \dfrac{\alpha + n}{\alpha + \beta + n}
\end{align}
%
and
%
\begin{align}
    G_j^k & \equiv {_2F_1}\left(j + 1, \alpha + k; \alpha + \beta + k; -\dfrac{c_1}{1 + c_0}\right)
    \quad.
\end{align}
%
Note that for fixed $\alpha$, $\beta$, $c_0$, and $c_1$, we need only compute
$G_0^0$, $G_1^0$, $G_0^1$, and $G_1^1$ directly, since the remaining terms may be
obtained recursively:
%
\begin{align}
    \label{eq:Grec}
    G_j^k & =
    \bigg[
        \dfrac{(\alpha + \beta + k - j)(1 + c_0)}{j(1 + c_0 + c_1)}
        \bigg] G_{j - 2}^k
    \nonumber
    \\[0.75em]
          &
    + \hspace{1.5pt}
    \bigg[
        -\dfrac{(\alpha + \beta - 2j + k)(1 + c_0) + (\alpha - j + k)c_1}
        {j(1 + c_0 + c_1)}
        \bigg]
    G_{j - 1}^k
    \\[1.5em]
    G_j^k & =
    \bigg[
        \frac{(\alpha + \beta + k - 2)(1 + c_0)}
        {\lambda_{k - 1}(\alpha + \beta - j + k - 2)c_1}
        \bigg]
    G_{j}^{k - 2}
    \nonumber
    \\[0.75em]
          & + \hspace{1.5pt}
    \bigg[
        -\frac{\alpha - (\alpha + k)c_1 + \beta + k + (\alpha + \beta + k - 2)c_0 + (j + 2)c_1 - 2}
        {\lambda_{k-1} (\alpha + \beta - j + k - 2)c_1}
        \bigg]
    G_{j}^{k - 1}
    \quad.
\end{align}
%

@@

We may again use Equations~(\ref{eq:s}) and (\ref{eq:pdf_r}) to write the

@@

\section{The Contrast Integrals: \lowercase{$\mathbf{e_2}$} and $\mathbf{E_2}$}
\label{sec:contrast}
%
\subsection{Functional form}
\label{sec:contrast-function}
Since the spot function $\mathbf{s}$ (Equation~\ref{eq:s}) is normalized
to $-1$, we may simply scale it by the contrast $\xi$ to obtain a spot
whose peak intensity is $-\xi$.
Assuming the baseline (unspotted) stellar intensity is unity, $\xi$
is the fractional decrease in the brightness relative to the stellar
baseline: i.e., the spot contrast.
%

@@

\subsection{First moment}
\label{sec:contrast-mom1}
The first moment of the spot contrast distribution is given by
Equation~(\ref{eq:e2}), which may easily be solved analytically:
%
\begin{align}
    \mathbf{e_2}(\pmb{\theta}_b, \mathbf{e_1})
     & =
    \int_{-\infty}^1
    \xi \,
    \mathbf{e_1} \,
    p(\xi \, \big| \, \pmb{\theta}_{\xi}) \,
    \mathrm{d}\xi
    \nonumber
    \\
     & =
    1 - \exp\left[ \mu + \frac{1}{2}\nu\right] \mathbf{e_1}
    \quad.
\end{align}
%

>>>>

    \mathbf{x} = \left( \xi \,\, \lambda \,\, \phi \,\, \rho \right)^\top

@@

    \mathbf{s}(\rho)

@@

where $\xi$ is the contrast of a spot,
$\lambda$ is its longitude, $\phi$ is its latitude,
and $\rho$ is its radius.
The vector function $\mathbf{s}(\rho)$

@@

    p(\rho \, \big| \, \pmb{\theta}_{\rho})

@@

    \pmb{\theta}_{\rho} \right)^\top

@@

    \mathbf{e_1}(\pmb{\theta}_\rho)

@@

    \mathbf{s}(\rho) \,
    p(\rho \, \big| \, \pmb{\theta}_{\rho}) \,
    \mathrm{d}\rho

@@

    \mathbf{e_2}(\pmb{\theta}_\phi, \mathbf{e_1})

@@

    \mathbf{e_3}(\pmb{\theta}_\lambda, \mathbf{e_2})

@@

    \mathbf{e_4}(\pmb{\theta}_\xi, \mathbf{e_3})

@@

    \mathbf{E_1}(\pmb{\theta}_\rho)

@@

    \mathbf{s}(\rho) \, \mathbf{s}^\top(\rho) \,
    p(\rho \, \big| \, \pmb{\theta}_{\rho}) \,
    \mathrm{d}\rho

@@

    \mathbf{E_2}(\pmb{\theta}_\phi, \mathbf{E_1})

@@

    \mathbf{E_3}(\pmb{\theta}_\lambda, \mathbf{E_2})

@@

    \mathbf{E_4}(\pmb{\theta}_\xi, \mathbf{E_3})
    p(\xi \, \big| \, \pmb{\theta}_\xi)

@@

%
\section{The Size Integrals: \lowercase{$\mathbf{e_1}$} and $\mathbf{E_1}$}
\label{sec:size}
%
\subsection{Functional form}
%

\subsubsection{$l_{\mathrm{max}} = \infty$}
\label{sec:size-function}
%
We adopt the following expression for the $n^{\mathrm{th}}$ term in $\mathbf{s}$
in the expansion of a dark, unit contrast circular spot at
$\lambda = \phi = 0$:
%
\begin{align}
    \label{eq:sinf}
    s_{n}^\infty(\rho) =
    \begin{cases}
        -\dfrac{\rho}{2(1 + \rho)}
         & l = m = 0
        \\[1em]
        -\dfrac{\rho \left( 2 + \rho \right)}
        {2 \sqrt{2l + 1} (1 + \rho)^{l + 1}}
         & l > 0, \, m = 0
        \\[1em]
        0
         & \mathrm{otherwise}
    \end{cases}
\end{align}
%
where
$l = l(n), m = m(n)$ (Equation~\ref{eq:lm}),
$\delta$ is the Kronecker delta,
$\rho \in [0, \infty)$ is the spot radius,
and the $\infty$ superscript denotes the fact that this expression
is valid in the limit $l_{\mathrm{max}} \rightarrow \infty$
(more on this below).
Equation~(\ref{eq:sinf}) is convenient because it satisfies
five important properties:
%
\begin{enumerate}[itemsep=2pt,parsep=1pt,label=\textbf{\arabic*}]
    \item The surface intensity is azimuthally symmetric about the spot center
    \item The surface intensity monotonically increases away from the spot center
    \item The surface intensity at the spot center is $-1$
    \item The surface intensity at the antipode of the spot center is zero
    \item The size of the spot increases monotonically with $\rho$
\end{enumerate}
%
These properties may be demonstrated by considering the
expression for the surface intensity at a given polar angle $\theta$ and
azimuth $\varphi$:
%
\begin{align}
    \begin{split}
        I(\theta, \varphi)
        & =
        \sum\limits_{n=0}^\infty
        s_{n}^\infty Y_{n}(\theta, \varphi) \\
        & =
        \sum\limits_{n=0}^\infty
        s_{n}^\infty \sqrt{2l + 1} \delta_{m0} P_l(\cos\theta)
    \end{split}
\end{align}
%
where $Y_n$ is the spherical harmonic of degree $l(n)$ and order $m(n)$
(see Equation~\ref{eq:lm}),
$P_l$ is the Legendre polynomial of degree $l$,
and we have implicitly
assumed a normalization such that the integral of our expansion over
the unit sphere is $4\pi$.
Note that the expression above is independent of the azimuth $\varphi$,
a consequence of the fact that all harmonics with $m \ne 0$ are zero; this
expansion is therefore azimuthally symmetric about the spot center, as
stated in \textbf{1}.
%
Combining the above expression with Equation~(\ref{eq:sinf}) and
rearranging, we may write
%
\begin{align}
    \label{eq:Igen}
    I(\theta, \varphi) =
    I(\theta) =
    \dfrac{\rho}{2}
    -
    \dfrac{\rho \left( 2 + \rho \right)}{2 (1 + \rho)}
    \sum\limits_{l=0}^\infty \left(\dfrac{1}{1 + \rho}\right)^l P_l(\cos\theta)
    \quad.
\end{align}
%
The summation in Equation~(\ref{eq:Igen}) has a closed-form expression in
terms of the generating function of the Legendre polynomials:
%
\begin{align}
    \label{eq:gen}
    \sum\limits_{l=0}^\infty t^l P_l(\cos\theta) = \frac{1}{\sqrt{1 + t^2 - 2 t \cos\theta}}
    \quad,
\end{align}
%
so we may express the intensity as a function of polar angle
in the fairly simple form
%
\begin{align}
    \label{eq:Ifinal}
    I(\theta) & = A - \frac{B}{\sqrt{C - \cos\theta}}
    \quad,
    %
    \\
    \intertext{where}
    %
    \begin{split}
        A & = \dfrac{\rho}{2}                      \\
        B & = \rho (2 + \rho) \sqrt{\dfrac{1}{8 + 8 \rho}} \\
        C & = \dfrac{1 + (1 + \rho)^2}{2 + 2 \rho}
    \end{split}
\end{align}
%
are positive constants.

Differentiating Equation~(\ref{eq:Ifinal}) with respect to $\theta$, we have
%
\begin{align}
    \label{eq:Ideriv}
    \dfrac{\mathrm{d}I(\theta)}{\mathrm{d}\theta} & =
    -\frac{B\sin\theta}{2(C - \cos\theta)^\frac{3}{2}}
    \quad,
\end{align}
%
which is zero only for $\theta = 0$ (for which $I(\theta)$ is
minimized) and $\theta = \pi$ (for which it is maximized). The intensity
therefore increases monotonically from the spot center to the antipode,
as stated in \textbf{2}. The value at the minimum is
%
\begin{align}
    \begin{split}
        I_{\mathrm{min}} & = A - \dfrac{B}{\sqrt{C - 1}} \\
        & = -1
        \quad,
    \end{split}
\end{align}
%
as stated in \textbf{3}, and the value at the maximum is
%
\begin{align}
    \begin{split}
        I_{\mathrm{max}} & = A - \dfrac{B}{\sqrt{C + 1}} \\
        & = 0
        \quad,
    \end{split}
\end{align}
%
as stated in \textbf{4}.
Finally, to show \textbf{5}, let us compute the half width at half minimum
$\Delta\theta$ of the intensity profile:
%
\begin{align}
    A - \dfrac{B}{\sqrt{C - \cos{\Delta\theta}}} =
    -\dfrac{1}{2}
\end{align}
%
Solving for $\Delta\theta$ yields
%
\begin{align}
    \label{eq:hwhm}
    \Delta\theta =
    \cos^{-1} \left[ \dfrac{2 + 3 \rho (2 + \rho)}{2 (1 + \rho)^3} \right]
    \quad.
\end{align}
%
Differentiation with respect to $r$ yields
%
\begin{align}
    \dfrac{\mathrm{d}\Delta\theta}{\mathrm{d}\rho} =
    \frac{3}{\left(1 + \rho\right)
        \sqrt{\left(1 + 2 \rho\right)
            \left(3 + 2 \rho\right)}}
    \quad,
\end{align}
%
which is positive definite for all $\rho > 0$.

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/spot_expansion.pdf}
        \oscaption{spot_expansion}{%
            \emph{Top.}
            Polar intensity profiles for spots with different normalized
            radii $\rho$ in the range $(0, 1]$, computed at spherical harmonic
            degree $l_{\mathrm{max}} = \LMAX$.
            \emph{Bottom.}
            The width $\Delta\theta$
            (Equation~\ref{eq:hwhm}) of the
            spot as a function of the radius parameter $r$ (left panel)
            and the normalized radius $\rho$ (right panel), computed for
            $l_{\mathrm{max}} = \LMAX$.
            \label{fig:spot_expansion}
        }
    \end{centering}
\end{figure}

\subsubsection{Finite $l_{\mathrm{max}}$}
%
It is important to note that the
properties of the spot expansion described above
(in particular its monotonicity and values at the spot center and antipode)
are inherited from the generating function of the Legendre polynomials
(Equation~\ref{eq:gen}). These properties are therefore only rigorously
true when the expansion is taken to spherical
harmonic degree $l_{\mathrm{max}} = \infty$. Expansions truncated to finite
$l_{\mathrm{max}}$ will in general experience ringing and a spot amplitude
whose (absolute) value is in general smaller than unity.

To mitigate these issues, we will do two things: we will impose a minimum
radius $r_{\mathrm{min}}$ to prevent highly oscillatory behavior within
the domain of our function; and we will scale the spot expansion
by an overall amplitude factor so that
the peak spot intensity is as close to (negative) unity as possible
everywhere within the domain.
We find that this can be accomplished by expressing the
$n^{\mathrm{th}}$ term in the spot expansion $\mathbf{s}$ as
%
\begin{align}
    s_n(\rho) = s_n^\infty\left(r\right) \left(1 + c_2 r^{-1} \left(1 + r\right) ^ {-c_3}\right)
\end{align}
%
where
%
\begin{align}
    r \equiv c_0 + c_1\rho
\end{align}
%
is a rescaled radius and $c_0, c_1, c_2, c_3$ are constants at a given
value of $l_{\mathrm{max}}$.
%
Plugging this into Equation~(\ref{eq:sinf}), we have
%
\begin{align}
    \label{eq:s}
    s_{n}(\rho) =
    \begin{cases}
        -\dfrac{r}{2(1 + r)} - \dfrac{c_2}{2(1 + r)^{c_3 + 1}}
         & l = m = 0
        \\[1em]
        -\dfrac{r \left( 2 + r \right)}
        {2 \sqrt{2l + 1} (1 + r)^{l + 1}}
        - \dfrac{c_2\left( 2 + r \right)}
        {2 \sqrt{2l + 1} (1 + r)^{c_3 + l + 1}}
         & l > 0, \, m = 0
        \\[1em]
        0
         & \mathrm{otherwise}
    \end{cases}
\end{align}
%
Note that in the limit $l_{\mathrm{max}} \rightarrow \infty$, we may set
$c_0 = 0$, $c_1 = 1$, and $c_2 = 0$ to recover the original parametrization.
At finite $l_{\mathrm{max}}$, however, we solve for the $c_n$ numerically,
by requiring the following conditions:

\xxx{TODO...}

@@

\subsection{First moment}
\label{sec:size-mom1}
%
The first moment of $\mathbf{s}$ is given by Equation~(\ref{eq:e1}).
We may use Equations~(\ref{eq:sinf}) and (\ref{eq:pdf_r}) to write the
$n^{\mathrm{th}}$ term of $\mathbf{{e_1}}(\pmb{\theta}_r)$ as
%
\begin{align}
    {e_1}_n(\alpha, \beta)
     & =
    \resizebox{.75\hsize}{!}{$
            \begin{dcases}
                -\dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
                \int\limits_0^1
                \dfrac{
                    (c_0 + c_1 r)
                    r^{\alpha - 1}
                    (1 - r)^{\beta - 1}
                }{2 (1 + c_0 + c_1 r)}
                \mathrm{d} r
                 &
                \qquad
                l = m = 0    \\[2em]
                -\dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
                \int\limits_0^1
                \dfrac{(c_0 + c_1 r) \left( 2 + c_0 + c_1 r \right)r^{\alpha - 1}
                (1 - r)^{\beta - 1}}
                {2 \sqrt{2l + 1} (1 + c_0 + c_1 r)^{l + 1}}
                \mathrm{d} r
                 &
                \qquad
                l > 0, m = 0 \\[2em]
                0
                 &
                \qquad m \ne 0
                \quad.
            \end{dcases}
        $}
\end{align}
%
Thanks to the dependence of the spherical harmonic coefficients on only
powers of $r$ and $(1 + c_0 + c_1 r)$, the integrals above may be expressed in closed
form in terms of the hypergeometric function ${_2F_1}$:
%
\begin{align}
    {e_1}_n(\alpha, \beta)
     & =
    \resizebox{.75\hsize}{!}{$
            \begin{dcases}
                -
                \dfrac{1}{2(1 + c_0)}
                \bigg[c_0H_0^0 + c_1 H_0^1\bigg]
                 &
                \qquad
                l = m = 0    \\[2em]
                -\dfrac{1}{2\sqrt{2l + 1} (1 + c_0)^{l+1}}
                \bigg[
                    c_0(2+c_0)H_l^0
                    +
                    2c_1(1 + c_0)H_l^1
                    +
                    c_1^2 H_l^2
                    \bigg]
                 &
                \qquad
                l > 0, m = 0 \\[2em]
                0
                 &
                \qquad m \ne 0
            \end{dcases}
        $}
\end{align}
%
where we define
%
\begin{align}
    H_j^k & \equiv \left(\prod_{n=0}^{k-1} \lambda_n\right) G_j^k
    \quad.
\end{align}
%
with
%
\begin{align}
    \lambda_n & \equiv \dfrac{\alpha + n}{\alpha + \beta + n}
\end{align}
%
and
%
\begin{align}
    G_j^k & \equiv {_2F_1}\left(j + 1, \alpha + k; \alpha + \beta + k; -\dfrac{c_1}{1 + c_0}\right)
    \quad.
\end{align}
%
Note that for fixed $\alpha$, $\beta$, $c_0$, and $c_1$, we need only compute
$G_0^0$, $G_1^0$, $G_0^1$, and $G_1^1$ directly, since the remaining terms may be
obtained recursively:
%
\begin{proof}{test_hypgeo}
    \label{eq:Grec}
    \begin{split}
        G_j^k & =
        \bigg[
            \dfrac{(\alpha + \beta + k - j)(1 + c_0)}{j(1 + c_0 + c_1)}
            \bigg] G_{j - 2}^k
        \\[0.75em]
        &
        + \hspace{1.5pt}
        \bigg[
            1 - \dfrac{(\alpha + \beta + k - j)(1 + c_0) + (\alpha + k)c_1}
            {j(1 + c_0 + c_1)}
            \bigg]
        G_{j - 1}^k
        \\[1.5em]
        G_j^k & =
        \bigg[
            \frac{(\alpha + \beta + k - 2)(1 + c_0)}
            {(\alpha + \beta - j + k - 2)\lambda_{k - 1}c_1}
            \bigg]
        G_{j}^{k - 2}
        \\[0.75em]
        & + \hspace{1.5pt}
        \bigg[
            \frac{1}{\lambda_{k - 1}}
            -\frac{(\alpha + \beta + k - 2)(1 + c_0) + \beta c_1}
            {(\alpha + \beta - j + k - 2)\lambda_{k-1}c_1}
            \bigg]
        G_{j}^{k - 1}
        \quad.
    \end{split}
    \raisetag{7.5em}
\end{proof}
%

@@

We may again use Equations~(\ref{eq:sinf}) and (\ref{eq:pdf_r}) to write the

@@

\section{The Latitude Integrals: \lowercase{$\mathbf{e_2}$} and $\mathbf{E_2}$}
\label{sec:latitude}
\xxx{TODO.}

\section{The Longitude Integrals: \lowercase{$\mathbf{e_3}$} and $\mathbf{E_3}$}
\label{sec:longitude}
\xxx{TODO.}

\section{The Contrast Integrals: \lowercase{$\mathbf{e_4}$} and $\mathbf{E_4}$}
\label{sec:contrast}
%
\subsection{Functional form}
\label{sec:contrast-function}
Since the spot function $\mathbf{s}$ (Equation~\ref{eq:sinf}) is normalized
to $-1$, we may simply scale it by the contrast $\xi$ to obtain a spot
whose peak intensity is $-\xi$.
Assuming the baseline (unspotted) stellar intensity is unity, $\xi$
is the fractional decrease in the brightness relative to the stellar
baseline: i.e., the spot contrast.
%

@@

\subsection{First moment}
\label{sec:contrast-mom1}
The first moment of the spot contrast distribution is given by
Equation~(\ref{eq:e4}), which may easily be solved analytically:
%
\begin{align}
    \mathbf{e_4}(\pmb{\theta}_\xi, \mathbf{e_3})
     & =
    \int_{-\infty}^1
    \xi \,
    \mathbf{e_3} \,
    p(\xi \, \big| \, \pmb{\theta}_{\xi}) \,
    \mathrm{d}\xi
    \nonumber
    \\
     & =
    \left(1 - \exp\left[ \mu + \frac{1}{2}\nu\right]\right) \mathbf{e_3}
    \quad.
\end{align}
%

\subsection{Second moment}
\label{sec:contrast-mom2}
The second moment of the spot contrast distribution is given by
Equation~(\ref{eq:E4}), which also evaluates to a simple closed form:
%
\begin{align}
    \mathbf{E_4}(\pmb{\theta}_\xi, \mathbf{E_3})
     & =
    \int_{-\infty}^1
    \xi^2 \,
    \mathbf{E_3} \,
    \mathbf{E_3}^\top \,
    p(\xi \, \big| \, \pmb{\theta}_{\xi}) \,
    \mathrm{d}\xi
    \nonumber
    \\
     & =
    \left(1 - 2\exp\bigg[ \mu + \frac{1}{2}\nu\bigg]
    + \exp\bigg[ 2\mu + 2\nu\bigg]\right)
    \mathbf{E_3} \,
    \mathbf{E_3}^\top
    \quad.
\end{align}
